Supplementary Materials: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus

### 2024-01-31 supplementary_thev_trxptome.Rmd
made standalone fig6-10

---
title: "Supplementary Materials: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus"
output:
  word_document: default
  pdf_document: default
geometry: margin=1in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
editor_options:
  chunck_output_type: console
---
\vspace{5mm}

@@

## Supplementary Table 1A

```{r Sup Table 1A}
set_flextable_defaults(font.size = 8)
make_reg_stats_table <- function(tp_table){
  return(tp_table %>%
    select(-junc_freq) %>% 
    mutate(region = ifelse(is.na(region), "Unassigned", region)) %>% 
    flextable() %>% 
    theme_zebra() %>% 
    set_header_labels(timepoint = "Time", region = "Region", strand = "Strand",
                      sum_reads_reg = "Total Reads", perc_reg = "Percentage") %>% 
    flextable::width(width = 0.8) %>% 
    flextable::align(align = "center", part = "all") %>%
    flextable::set_table_properties(layout = "fixed", align = "left",
                       opts_pdf = list(caption_repeat = FALSE),
                       opts_word = list(split = F))
  )
}
make_reg_stats_table(tp_reg_expr_12) %>%
  set_caption("Table 1a: Most Transcriptionally Active Regions of THEV at 12h.p.i")

@@

## Supplementary Table 1B

```{r Sup Table 1B}
set_flextable_defaults(font.size = 8)
make_reg_stats_table(tp_reg_expr_24) %>%
  set_caption("Table 1b: Most Transcriptionally Active Regions of THEV at 24h.p.i")
```

## Supplementary Table 1C

```{r Sup Table 1C}
set_flextable_defaults(font.size = 8)
make_reg_stats_table(tp_reg_expr_72) %>%
  set_caption("Table 1c: Most Transcriptionally Active Regions of THEV at 72h.p.i")
```

@@

supp_pcr_meth_tab %>% 
  select(-valid_status) %>% 
flextable() %>%
  theme_zebra() %>%
  set_header_labels(trxpt_id = "Transcript ID", region = "Region", num_exons = "Number of Exons",
                    full_trxpt = "Full Transcript", exon1 = "Exon 1", exon2 = "Exon 2",
                    exon3 = "Exon 3", exon4 = "Exon 4", exon5 = "Exon 5", exon6 = "Exon 6",
                    exon7 = "Exon 7", forwardP = "Forward Primer", reverseP = "Reverse Primer",
                    gel_image = "Agarose Gel") %>% 
  flextable::fontsize(j = c("full_trxpt", "exon1", "exon2", "exon3",
                            "exon4", "exon5", "exon6", "exon7",
                            "forwardP", "reverseP"), size = 3) %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::width(., width = 0.35) %>% 
  colformat_image(j = "gel_image", i = c(1:3, 5:26, 28:30),
                  width = 1.1, height = 1) %>%
  flextable::width(j = ~forwardP, width = 1.1) %>%
  flextable::width(j = ~reverseP, width = 1.1) %>%
  flextable::width(j = ~gel_image, width = 1.15) %>%
  # flextable::height(height = 0, part = "header") %>% 
  footnote(., i = c(1:26, 28:30), j = 12, value = as_paragraph(c("Primer binds inside first exon")),
           ref_symbols = c("a"), part = "body", inline = T) %>%
  footnote(., i = c(1:7, 9:18, 21:26, 28, 29), j = 13, value = as_paragraph(c("Primer binds inside terminal exon")), ref_symbols = c("b"), part = "body", inline  = T) %>% 
  # transcripts too long to validate with one primer pair
  footnote(., i = c(8,19, 20, 30), j = 13, value = as_paragraph(c("Primer binds inside fourth exon")),
           ref_symbols = c("c"), part = "body", inline = T) %>% 
  footnote(., i = c(8), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_7 due to identical splicing")), ref_symbols = c("I"), part = "body", inline = T) %>%
  footnote(., i = c(10), j = 14, value = as_paragraph(c("Agarose gel identical to last 3 exons of TRXPT_10 due to identical splicing")), ref_symbols = c("II"), part = "body", inline = T) %>%
  footnote(., i = c(12), j = 14, value = as_paragraph(c("Agarose gel identical to last 4 exons of TRXPT_11 due to identical splicing")), ref_symbols = c("III"), part = "body", inline = T) %>% 
  footnote(., i = c(16), j = 14, value = as_paragraph(c("Agarose gel dentical to TRXPT_23 due to identical splicing")), ref_symbols = c("IV"), part = "body", inline = T) %>% 
  footnote(., i = c(19), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_9 due to identical splicing")), ref_symbols = c("V"), part = "body", inline = T) %>% 
  footnote(., i = c(20), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_14 due to identical splicing")), ref_symbols = c("VI"), part = "body", inline = T) %>%
  flextable::set_table_properties(layout = "fixed", align = "left",
                       opts_pdf = list(caption_repeat = F),
                       opts_word = list(split = F)) %>%
  set_caption("Table 1: Agarose Gels Showing PCR Amplification of THEV cDNA With Gene-Specific Primers")
```

>>>>

---
title: "Supplementary Materials: Elucidating the Transcriptome of Turkey Hemorrhagic Enteritis Virus"
output: 
  officedown::rdocx_document:
    reference_docx: style_word_output.docx
  pdf_document: default
geometry: margin=1in
font-size: 11pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
editor_options:
  chunck_output_type: console
---
\vspace{5mm}

@@

## Supplementary Table S1A

```{r Sup Table S1A}
set_flextable_defaults(font.size = 8)
make_reg_stats_table <- function(tp_table){
  return(tp_table %>%
    select(-junc_freq) %>% 
    mutate(region = ifelse(is.na(region), "Unassigned", region)) %>% 
    flextable() %>% 
    theme_zebra() %>% 
    set_header_labels(timepoint = "Time", region = "Region", strand = "Strand",
                      sum_reads_reg = "Total Reads", perc_reg = "Percentage") %>% 
    flextable::width(width = 0.8) %>% 
    flextable::align(align = "center", part = "all") %>%
    flextable::set_table_properties(layout = "fixed", align = "left",
                       opts_pdf = list(caption_repeat = FALSE),
                       opts_word = list(split = F))
  )
}
make_reg_stats_table(tp_reg_expr_12) %>%
  set_caption("Table S1a: Most Transcriptionally Active Regions of THEV at 12h.p.i")

@@

## Supplementary Table S1B

```{r Sup Table S1B}
set_flextable_defaults(font.size = 8)
make_reg_stats_table(tp_reg_expr_24) %>%
  set_caption("Table S1b: Most Transcriptionally Active Regions of THEV at 24h.p.i")
```

## Supplementary Table S1C

```{r Sup Table S1C}
set_flextable_defaults(font.size = 8)
make_reg_stats_table(tp_reg_expr_72) %>%
  set_caption("Table S1c: Most Transcriptionally Active Regions of THEV at 72h.p.i")
```

@@

supp_pcr_meth_tab %>% 
  select(-valid_status) %>% 
flextable() %>%
  theme_zebra() %>%
  set_header_labels(trxpt_id = "Transcript ID", region = "Region", num_exons = "Number of Exons",
                    full_trxpt = "Full Transcript", exon1 = "Exon 1", exon2 = "Exon 2",
                    exon3 = "Exon 3", exon4 = "Exon 4", exon5 = "Exon 5", exon6 = "Exon 6",
                    exon7 = "Exon 7", forwardP = "Forward Primer", reverseP = "Reverse Primer",
                    gel_image = "Agarose Gel") %>% 
  flextable::fontsize(j = c("full_trxpt", "exon1", "exon2", "exon3",
                            "exon4", "exon5", "exon6", "exon7",
                            "forwardP", "reverseP"), size = 3) %>%
  flextable::align(align = "center", part = "all") %>%
  flextable::width(., width = 0.35) %>% 
  colformat_image(j = "gel_image", i = c(1:3, 5:26, 28:30),
                  width = 1.1, height = 1) %>%
  flextable::width(j = ~forwardP, width = 1.1) %>%
  flextable::width(j = ~reverseP, width = 1.1) %>%
  flextable::width(j = ~gel_image, width = 1.15) %>%
  # flextable::height(height = 0, part = "header") %>% 
  footnote(., i = c(1:26, 28:30), j = 12, value = as_paragraph(c("Primer binds inside first exon")),
           ref_symbols = c("a"), part = "body", inline = T) %>%
  footnote(., i = c(1:7, 9:18, 21:26, 28, 29), j = 13, value = as_paragraph(c("Primer binds inside terminal exon")), ref_symbols = c("b"), part = "body", inline  = T) %>% 
  # transcripts too long to validate with one primer pair
  footnote(., i = c(8,19, 20, 30), j = 13, value = as_paragraph(c("Primer binds inside fourth exon")),
           ref_symbols = c("c"), part = "body", inline = T) %>% 
  footnote(., i = c(8), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_7 due to identical splicing")), ref_symbols = c("I"), part = "body", inline = T) %>%
  footnote(., i = c(10), j = 14, value = as_paragraph(c("Agarose gel identical to last 3 exons of TRXPT_10 due to identical splicing")), ref_symbols = c("II"), part = "body", inline = T) %>%
  footnote(., i = c(12), j = 14, value = as_paragraph(c("Agarose gel identical to last 4 exons of TRXPT_11 due to identical splicing")), ref_symbols = c("III"), part = "body", inline = T) %>% 
  footnote(., i = c(16), j = 14, value = as_paragraph(c("Agarose gel dentical to TRXPT_23 due to identical splicing")), ref_symbols = c("IV"), part = "body", inline = T) %>% 
  footnote(., i = c(19), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_9 due to identical splicing")), ref_symbols = c("V"), part = "body", inline = T) %>% 
  footnote(., i = c(20), j = 14, value = as_paragraph(c("Agarose gel identical to TRXPT_14 due to identical splicing")), ref_symbols = c("VI"), part = "body", inline = T) %>%
  flextable::set_table_properties(layout = "fixed", align = "left",
                       opts_pdf = list(caption_repeat = F),
                       opts_word = list(split = F)) %>%
  set_caption("Agarose Gels Showing PCR Amplification of THEV cDNA With Gene-Specific Primers")
```
